# Basic R for Graphics"

###  Scott Karr
###  HW4 School Expenditures by State
###  11.29.2015
### Packages:  ggplot2, data.tables

##  This data frame contains the following columns:
####  education Per-capita education expenditures, dollars.
####  income Per-capita income, dollars.
####  young Proportion under 18, per 1000.
####  urban Proportion urban, per 1000.

# Setup and Load data
1. Load Anscombe education expenditure data by state.

```{r}
## Load Data Frame from website
require(data.table)
require(ggplot2)

AnscombeUrl <- "http://vincentarelbundock.github.io/Rdatasets/csv/car/Anscombe.csv"
df_Anscombe <- read.table(file = AnscombeUrl, header = TRUE, sep = ",")
dt_Anscombe <- data.table(df_Anscombe)
```

## Generate Descriptive Statistics
2. Generate summary level descriptive statistics:

```{r}
head(df_Anscombe)
str(df_Anscombe)
```

## Prepare Dataset for Graphics
3. Rename columns as needed

```{r}
## Rename "state" column
##setnames(df_Anscombe, old=c(""), new=c("state"))
colnames(df_Anscombe)[c(1)] <- c("state")
```


4.  Histogram showing count of states by increasing per-capita-spending by state
```{r}
ggplot(data = df_Anscombe) + geom_histogram(aes(x = education))
```

5. Plot per-capita-spending to per-capita income grouped by state
```{r}
g <- ggplot(df_Anscombe, aes(x = education, y = income)) + geom_point()
g <- g + geom_point(aes(color = state)) + facet_wrap(~state)
g
```